\documentclass[11pt]{article} %Sets the default text size to 11pt and class to article.
%------------------------Dimensions--------------------------------------------
\topmargin=-0.6in %length of margin at the top of the page (1 inch added by default)
\oddsidemargin=-0.5in %length of margin on sides for odd pages
\evensidemargin=0in %length of margin on sides for even pages
\textwidth=7.0in %How wide you want your text to be
\marginparwidth=0.5in
\headheight=0pt %1in margins at top and bottom (1 inch is added to this value by default)
\headsep=0pt %Increase to increase white space in between headers and the top of the page
\textheight=9.8in %How tall the text body is allowed to be on each page
%-------------------------End Dimensions-----------------------------------------

%------------------------Packages-------------------------------------------------%

\usepackage[urlbordercolor={1 1 1}]{hyperref}
%-------------------------End Packages---------------------------------------------%

\begin{document}
\pagenumbering{gobble}
\centerline{{\Huge \sc Joe Jean}}  %Makes whatever text you put in parenthesis move to the center
%Prevents the following text from being indented
%This is the same as a return in Latex
\centerline{Abu Dhabi, UAE}
\centerline{(971).50.106.7468 \textbar \hspace{2pt}\href{mailto:joe.jean@nyu.edu}{joe.jean@nyu.edu} \textbar \hspace{2pt}\url{www.joejean.net} \textbar \hspace{2pt}\url{https://github.com/joejean} } 
\noindent
\rule{\textwidth}{1pt}\bigskip
%\line(1,0){470}\\

\noindent{\Large \bf EDUCATION}\medskip

\noindent \centerline{\normalsize \bf New York University Abu Dhabi \hfill \textbf{Expected May 2016} }
Bachelor of Science in Computer Science. GPA: 3.47 / 4.00\\

\noindent{\Large \bf EXPERIENCE} \medskip

\noindent \centerline{\large \textbf{\textit{Recurser}}, \textbf {Recurse Center}, New York, USA \hfill \textbf{Summer 2015}}
\begin{itemize}\itemsep-0.2em
  \item Wrote a Lisp interpreter in C. 
  \item Built a WYSGI web server in Python.
  \item Built a URL shortener using Python, Flask, SQLite and Bootstrap.
\end{itemize}
\noindent \centerline{\large \textbf{\textit{Summer Research Assistant}}, \textbf {NYU CIMS}, New York, USA \hfill \textbf{Summer 2014}}
\begin{itemize}\itemsep-0.2em
  \item Implemented a system which recommends stores that are good fits for a given shopping center.
  \item Programmed Python scripts to scrape the web for a list of shopping centers and their stores in the United States.
\end{itemize}
\medskip

\noindent{\Large \bf PROJECTS}\vspace{0.05in}

\noindent \centerline{\normalsize \textbf{Food Ordering Website}, \url{http://www.chipin.ae} \hfill \textbf{Spring 2015}}
\begin{itemize}
  \item Served as the lead developer of a web application for a food delivery startup. The application's technology stack consists of: Node.js with Express, Bootstrap, jQuery, MongoDB and Heroku.
\end{itemize}
\noindent \centerline{\normalsize \textbf{PumpMeUp}, \url{http://pumpmeup.herokuapp.com/} \hfill \textbf{Fall 2014}}
\begin{itemize}\itemsep-0.2em
  \item Built a positive quotes API. I also built a front end that allows users to search, add and like motivational quotes. The application's technology stack consists of: Express, Bootstrap, jQuery, and MongoDB.
\end{itemize}
\noindent \centerline{\normalsize \textbf{NYUAD Course Review Website}, \url{http://cr.sg.nyuad.org} \hfill \textbf{Summer 2013}}
\begin{itemize}\itemsep-0.2em
  \item Built and maintained a web application that allows more than 700 NYU Abu Dhabi students to read and write course reviews. The application's technology stack consists of: Flask, Bootstrap, jQuery, SQLAlchemy with PostgreSQL and Heroku.
\end{itemize}
\medskip

\noindent{\Large \bf SKILLS}
\begin{itemize}\itemsep-0.2em
  \item \textbf{Programming Languages:} Python, JavaScript, C.
  \item \textbf{Web and Internet Technologies:} Node.js, Express, Flask, HTML, CSS, Bootstrap, JSON, Web API, jQuery, Knockout.js.
  \item \textbf{Databases:} MySQL, PostgreSQL, SQLite, MongoDB.
  \item \textbf{Other Tools:} Windows (7, 8), Linux (Ubuntu), AWS, Heroku, CircleCI, Git, GitHub.
  \item \textbf{Languages:} Fluent in English, French, and Creole.
\end{itemize}
\medskip

\noindent{\Large \bf AWARDS} \medskip

\noindent \centerline{\normalsize  \textbf {HACK2040 Hackathon}, New York, USA \hfill \textbf{June 2015}}
\begin{itemize}\itemsep-0.2em
  \item Foursquare's Global Impact Prize
  \item CODE2040's Technically Difficult Prize
\end{itemize}
\end{document}